### 2016-03-11 paper/stereo.tex
Hang

\subsection{Swarm Fusion stereo}
We start with a simple depthmap stereo problem with standard unary and
pairwise terms. We employ submodular pairwise terms to make this stereo
represent relatively ``easy'' MRF inference problems.
%
Unary terms are computed as the average Normalized Cross Correlation
score between the reference image and the others inside a $7\times 7$
pixels window. Pairwise terms are simple Pottz model. The total energy
is defined by the sum of the two, while scaling the pairwise term by a
factor of \yasu{X value}.
%
We use images from the Middlebury stereo benchmark~\cite{middlebury_stereo}.

@@

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
stereo problems.  Our experiments have also supported this, where the
fusion method (i.e., the use of proposal generation) rather makes it slow
due to the overhead.  Therefore, we have chosen Parallel
Alpha Expansion~\cite{delong} and Hierarchical Fusion~\cite{delong,olga}
with graph-cuts optimization as the competing methods.

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
multi-way fusion), and the standard SF.
%
SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set to
2. SF-MF implies $\alpha+\beta=1$, where each thread iterates the step
of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so that it can take a
solution proposal in one step and a neighboring solution in the
next. For standard SF, we have used ($\alpha=1, \beta=1$).
%
%
%
%
To make the comparison simple, we restrict our proposal
generation to be constant-label proposals. Graph-cuts is used in fusing
a constant-label proposal as the energy is submodular. QPBO is used in
fusing a different solution from another thread as the energy is
non-submodular.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.

>>>>

\subsection{Swarm Fusion stereo}
We start with a simple depthmap stereo problem with standard unary and
pairwise terms. We employ submodular pairwise terms to make this stereo
represent relatively ``easy'' MRF inference problems.
%
Unary terms are computed as the average robust photoconsistancy
score~\cite{woodford} between the reference image and the others inside a $7\times 7$
pixels window.
\begin{equation}
  \text{\hang{equation to fill in}}
\end{equation}
Pairwise terms are simple truncated absolute label
difference with maximum label difference $\sigma_s=4$. The total energy is
defined by the sum of the two, while scaling the pairwise term by a
factor of $0.005$. For simplicity we don't enforce visibility constraint.

%
We performed our experiments on Book sequence from Middlebury stereo datasets.~\cite{middlebury_stereo}.

@@

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
stereo problems.  Our experiments have also supported this, where the
fusion method (i.e., the use of proposal generation) rather makes it slow
due to the overhead.\hang{Don't quite understand this sentence. Does the ``dominant'' means running time or energy? In my experiments, unary terms are pre-computed and are not counted into the running time}  Therefore, we have chosen Parallel
Alpha Expansion~\cite{delong} and Hierarchical Fusion~\cite{delong,olga}
with graph-cuts optimization as the competing methods.

add Alpha Expansion.
uniform and random splitting for parallel alpha expansion

@@

\noindent The three swarm architectures in Fig.~\ref{fig:model} have
been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
multi-way fusion), and the standard SF.
%
SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set to
2. SF-MF implies $\alpha+\beta=1$, where each thread iterates the step
of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so that it can take a
solution proposal in one step and a neighboring solution in the
next. For standard SF, we have used ($\alpha=1, \beta=1$).

after 4 iterations (alpha, beta),

%
%
%
%
To make the comparison simple, we restrict our proposal
generation to be constant-label proposals. Graph-cuts is used in fusing
a constant-label proposal as the energy is submodular. QPBO is used in
fusing a different solution from another thread as the energy is
non-submodular.
%
% Due to the lack of multi-way fusion, the swarm fusion architecture for
% the stereo problem is represented by the middle example at the bottom of
% Fig.~\ref{fig:model}.
